# DevDatProd_wk4

This is the github repo for Arnold Cross's week 4 project in the Johns Hopkins coursera class, Developing Data Products.  The project has two parts.  The first part is a shiny app published at https://arnoldcross.shinyapps.io/DevDatProd_wk4/.  The second part is a slideshow created in Rstudio Presentation.

The project is based on population data from the U.S. Census Bureau.  The data is explained at https://www.census.gov/data/developers/data-sets/popest-popproj/popest.html.

The following code downloads one population dataset but does not do anything with it.

```{r}
library(jsonlite)
library(magrittr)
library(leaflet)
censDat <- fromJSON("https://api.census.gov/data/2016/pep/population?get=POP,DATE,DATE_DESC&for=state:*")
```

Below is a download and mapping of the population centers.

The source link is at https://www.census.gov/geo/reference/centersofpop.html under [Data Files], click [Centers of Population by State:  2010].

```{r}
popCen <- read.csv("http://www2.census.gov/geo/docs/reference/cenpop2010/CenPop2010_Mean_ST.txt", stringsAsFactors=F)

stDF  <- data.frame(lat=popCen$LATITUDE, lng=popCen$LONGITUDE)
stDF %>% leaflet() %>% addProviderTiles(providers$OpenStreetMap) %>% addCircleMarkers()
```