# DeveDataProd_proj1

```{r}
library(jsonlite)
library(magrittr)
library(leaflet)
censDat <- fromJSON("https://api.census.gov/data/2016/pep/population?get=POP,DATE,DATE_DESC&for=state:*")
colnames(censDat) <- censDat[1,]
censDat <- censDat[2:nrow(censDat),]
```
The source link is at https://www.census.gov/data/developers/data-sets/popest-popproj/popest.html.



```{r}
popCen <- read.csv("http://www2.census.gov/geo/docs/reference/cenpop2010/CenPop2010_Mean_ST.txt", stringsAsFactors=F)
```
Text file containing population and mean centers of population by state/state equivalent entity for the 2010 Census. The record layout is:
- STATEFP:  2-character state FIPS code
- STNAME:  state name
- POPULATION:  2010 Census population tabulated for the state
- LATITUDE:  latitude coordinate for the center of population for the state
- LONGITUDE:  longitude coordinate for the center of population for the state

The source link is at https://www.census.gov/geo/reference/centersofpop.html under [Data Files].


```{r}
popCen <- read.csv("http://www2.census.gov/geo/docs/reference/cenpop2010/CenPop2010_Mean_ST.txt", stringsAsFactors=F)

stDF  <- data.frame(lat=popCen$LATITUDE, lng=popCen$LONGITUDE)
stDF %>% leaflet() %>% addProviderTiles(providers$OpenStreetMap) %>% addCircleMarkers()
```